RDF Constraint Types to Ensure High Data Quality

### 2015-04-29 paper/paper7/paper7.tex
evaluation

Data quality is not bad since only a small amount of the constraint violations are caused by error constraints
\emph{SBE} domain experts associated almost the half of the constraints with the severity levels $\mathcal{SL}_{0}$ (\emph{informational}) (47\%) and $\mathcal{SL}_{2}$ (\emph{error}) (45\%);
only 8.5\% are $\mathcal{SL}_{1}$ (\emph{warning}) constraints.
The violation of 80\% of the \emph{QB} constraints is very serious ($\mathcal{SL}_{2}$).
More than 50\% of the \emph{Disco} and \emph{SKOS} constraints, however, are assigned to the weakest default severity level ($\mathcal{SL}_{0}$).
For Disco, 1/6 of the constraint violations are serious.
Although, only 8.5\% of all constraints are $\mathcal{SL}_{1}$ constraints,
9 0f 10 constraint violations are caused by constraints associated with the default severity level $\mathcal{SL}_{1}$.
More than 50\% of all constraint violations thrown for \emph{Disco} data sets are not seen to be that significant ($\mathcal{SL}_{0}$).
Almost all constraint violations raised by \emph{QB} constraints and 59\% of the constraint violations caused by \emph{SKOS} constraints are classified as warnings ($\mathcal{SL}_{1}$).  
As this evaluation serves as indication for \emph{good} or \emph{bad} (meta)data quality, 
we conclude that
the metadata quality of all evaluated \emph{Disco} data sets is \emph{good} and that the metadata quality of all evaluated \emph{QB} and \emph{SKOS} data sets is \emph{satisfactory}.
\begin{hyp}
In general, data quality is very high.
The quality of data represented by established vocabularies is good,
as serious constraint violations rarely appear.
The quality of data represented by newly developed vocabularies, however, is worse,
as serious constraint violations occur partially.
For well-established vocabularies, the explicitly defined constraints are almost completely satisfied which demonstrates that constraint formulation in general works.
\end{hyp}

>>>>

63\% of all constraint violations are caused by warning constraints which are only 10\% of all constraints. 
Only 6\% of the constraint violations are caused by error constraints which are 49\% of all constraints.

\begin{hyp}
Data quality is good since only 6\% of the constraint violations are caused by error constraints which are 49\% of all constraints.
\end{hyp}

80\% of the \emph{QB} constraints are error constraints.
More than 50\% of the \emph{Disco} and \emph{SKOS} constraints, however, are informational constraints.

For Disco, 1/6 of the constraint violations are serious.
Although, only 8.5\% of all constraints are $\mathcal{SL}_{1}$ constraints,
9 0f 10 constraint violations are caused by constraints associated with the default severity level $\mathcal{SL}_{1}$.
More than 50\% of all constraint violations thrown for \emph{Disco} data sets are not seen to be that significant ($\mathcal{SL}_{0}$).
Almost all constraint violations raised by \emph{QB} constraints and 59\% of the constraint violations caused by \emph{SKOS} constraints are classified as warnings ($\mathcal{SL}_{1}$).  
As this evaluation serves as indication for \emph{good} or \emph{bad} (meta)data quality, 
we conclude that
the metadata quality of all evaluated \emph{Disco} data sets is \emph{good} and that the metadata quality of all evaluated \emph{QB} and \emph{SKOS} data sets is \emph{satisfactory}.
\begin{hyp}
In general, data quality is very high.
The quality of data represented by established vocabularies is good,
as serious constraint violations rarely appear.
The quality of data represented by newly developed vocabularies, however, is worse,
as serious constraint violations occur partially.
For well-established vocabularies, the explicitly defined constraints are almost completely satisfied which demonstrates that constraint formulation in general works.
\end{hyp}
